---
title: "ignyt"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ignyt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Let's start by loading the recommended packages, and set some initial parameters.
```{r setup, message = FALSE}

library(ignyt)

library(dplyr)
library(magrittr)
library(lubridate)
library(knitr)
library(tictoc)

# Set some document-wide parameters:
shift <- "am"
ps_test <- TRUE
```

## Examination allocation report

This report shows the daily allocation of radiological CT and MRI examinations to all  radiologists on a summarized and on an individual level. 

### Fetch data {.tabset}

We would usually connect to the reporting API (in our case 'ps' is short for PowerScribe), determine which shift we're assigning and fetch a worklist with one of the `fetch` commands:

```{r prep, eval = FALSE}
# Not run

if (hour(Sys.time()) < 12) {
  shift <- "am"
} else {
  shift <- "pm"
}

ps_auth()

register_ignyt_board()

worklist <- fetch_completed() %>%
  prep_worklist()
```

But for the purposes of this vignette, we will use the provided built-in test data:

```{r sim_fetch}

tic()
worklist <- sim_worklist(1) %>%
  prep_worklist()
```

Next, we simulate assignment (usually we would use `assign` instead of `sim_assign` and `shift_rads` instead of `sim_shift_rads`)

```{r sim_assign}

ct_att <- sim_shift_rads(1, "CT", shift)
cts <- worklist %>% divide_ct(ct_att, 2, bypass_ps = ps_test)
ct_att_unnested <- cts$assignments %>% sim_assign()
log_not_assigned_ct <- cts$not_assigned %>%
  bind_rows(ct_att_unnested %>% filter(assigned_status != "OK"))
ct_att_unnested %<>% filter(assigned_status == "OK")
# update_pin_bal(ct_att_unnested, test_pin = TRUE)

mr_att <- sim_shift_rads(1, "MR", shift)
mrs <- worklist %>%
  filter(!ris_accession_number %in% ct_att_unnested$ris_accession_number) %>% 
  divide_mr(mr_att, 2, bypass_ps = ps_test)
mr_att_unnested <- mrs$assignments %>% sim_assign()
log_not_assigned_mr <- mrs$not_assigned %>%
  bind_rows(mr_att_unnested %>% filter(assigned_status != "OK"))
mr_att_unnested %<>% filter(assigned_status == "OK")
# update_pin_bal(mr_att_unnested, test_pin = TRUE)

toc(log = TRUE, quiet = TRUE)
```

You may time the whole process and display the time to run to the user, in our case `r tic.log() %>% unlist() %>% stringr::str_extract("\\d+\\..\\d+ sec")`. Usually this will be longer due to SQL queries, built-in pauses between API requests etc.

Now we can inspect how the exams were divided:

#### MR

```{r mr_summary_tables, eval=FALSE}

mr_att_unnested %>%
  group_by(Name) %>%
  summarise(
    `Weighted exam units` = sum(exam_weighting),
    `Number of exams` = n()
  ) %>%
  kable()
```

#### CT

```{r ct_summary_tables, eval=FALSE}

ct_att_unnested %>%
  group_by(Name) %>%
  summarise(
    Shift = first(task_name),
    `Number of exams` = n(),
    `Weighted exam units` = sum(exam_weighting)
  ) %>%
  kable()
```

#### CT details

```{r ct_details, eval=FALSE}

ct_att_unnested %>%
  select(
    Name, task_name, ris_accession_number, ris_mrn,
    dmt.1:pref.3, state_code, ris_exam_end_dt,
    wet_read_request, exam_description, history, dmt, dmt_match
  ) %>%
  kable()
```

#### MRI details

```{r mr_details, eval=FALSE}

mr_att_unnested %>%
  select(
    Name, task_name, ris_accession_number, ris_mrn,
    dmt.1:dmt.4, state_code, ris_exam_end_dt, wet_read_request, exam_description, history, dmt
  ) %>%
  kable()
```

#### Not successfully allocated exams

```{r failures, eval=FALSE}
bind_rows(log_not_assigned_ct, log_not_assigned_mr) %>%
  filter(!is.na(assigned_status)) %>%
  bind_rows(log_not_assigned_ct, log_not_assigned_mr) %>%
  arrange(modality_code, wet_read_request, ris_exam_end_dt) %>%
  select(
    modality_code, ris_accession_number, ris_mrn, ris_exam_end_dt,
    wet_read_request, state_code, dmt, ps_status, assigned_status
  ) %>%
  kable()
```


#### Leftovers

```{r leftovers, eval=FALSE}

bind_rows(log_not_assigned_ct, log_not_assigned_mr) %>%
  filter(is.na(assigned_status)) %>%
  select(
    modality_code, ris_accession_number, ris_mrn, ris_exam_end_dt,
    wet_read_request, state_code, dmt, ps_status
  ) %>%
  DT::datatable()
```

Pin: Balance sheet

```{r balance, eval=FALSE}
if (nrow(pins::pin_find(name = "ignyt_balance_sheet_test")) > 0) {
  pins::pin_get("ignyt_balance_sheet_test", "rsconnect") %>%
    kable()
}
```
